Supplementary Materials

### 2018-12-11 Manuscript/sup_mat/sup_mat.Rmd
more updates to sup_mat

## Split-Half
Accuracy data is shown in Figure \ref{fig:fig1}. From this we can see that there are a number of outliers: 15, 25, 47, and 48 (NB: these may have changed with new labelling). These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials. This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.

```{r acc_plt, fig.cap = "Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

```{r rt_plt, fig.cap = "Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt <- ls_acc_RT %>%
  ggplot(aes(rt)) + 
  geom_histogram() + 
  theme_bw() +  
  facet_wrap(~targSide)
plt$labels$x <- "Response Time (msecs)"
plt2 <- ls_acc_RT %>%
  mutate(log2_RT = log2(rt)) %>%
  ggplot(aes(log2_RT)) + 
  geom_histogram() + 
  theme_bw() +
  facet_wrap(~ targSide)
plt2$labels$x <- "log2 Response Time"

>>>>

## Split-Half
Accuracy data is shown in Figure \ref{fig:acc_plt}. From this we can see that there are a number of outliers: 15, 25, 47, and 48 (NB: these may have changed with new labelling). These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials. This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.

```{r acc_plt, fig.cap = "\\label{fig:acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

```{r rt_plt, fig.cap = "\\label{fig:rt_plt} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt <- ls_acc_RT %>%
  ggplot(aes(rt)) + 
  geom_histogram() + 
  theme_bw() +  
  facet_wrap(~targSide)
plt$labels$x <- "Response Time (msecs)"
plt2 <- ls_acc_RT %>%
  mutate(log2_RT = log2(rt)) %>%
  ggplot(aes(log2_RT)) + 
  geom_histogram() + 
  theme_bw() +
  facet_wrap(~ targSide)
plt2$labels$x <- "log2 Response Time"
